Mendelian randomization for causal inference in genome-wide association studies

### 2022-03-02 mr-review.Rmd
added text about MVMR

>>>>

@schmidt_mendelian_2018 present BMRE, a Bayesian implementation of 
MR Egger. They apply weakly informative priors to the horizontal pleiotropy effect 
estimator in efforts to increase statistical power to detect a nonzero 
slope, i.e., the coefficient of the SNP instrument. They develop their method for two-sample MR with individual-level 
data. Simulations demonstrate that BMRE outperforms the MR Egger method while maintaining type I error rates in the examined scenarios. The authors emphasize a potential role for BMRE in 
MR sensitivity analysis.

@howey_bayesian_2020 use anchored Bayesian networks to

@sanderson_examination_2019 found that multivariable MR, where multiple exposures jointly 
cause an outcome, consistently estimates the effect of the exposures on the outcome. They 
examined multivariable MR with both individual-level data and GWAS summary statistics. 
@sanderson_examination_2019 also develop a generalized version of Cochran's Q test for 
quantifying SNP instrument strength and validity. However, this test requires knowledge of 
the covariances between the effects of the SNP instruments on the exposures. While these 
covariances could be estimated from individual-level data, such data are often unavailable in 
the GWAS setting. Importantly, the authors note that the estimands for multivariable MR nad MR 
differ; multivariable MR estimates the direct causal effects of each exposure on the outcome, 
while MR estimates the total causal effect of an exposure on the outcome.

@van_der_graaf_mendelian_2020
